Flooding of the Okavango Delta influences Connectivity for Dispersing African Wild Dogs

### 2022-11-29 Chapter_8/04_Manuscript/Manuscript.tex
Updated betweenness maps

Climate change is expected to critically impact the flood-pulsing cycles of the
Okavango delta and may therefore critically alter landscape connectivity in this
area. Besides a better understanding of the conservation needs for the African
wild dog, our study also presents a first step towards incorporating
environmental changes due to seasonality or climate change in dispersal and
connectivity analyses. Finally, our analysis demonstrates the usefulness of
individual-based dispersal simulations as a pertinent conservation tool to study
impacts of environmental change while accounting for dispersal movements.

>>>>

Climate change is expected to critically impact the flood-pulsing cycles of the
Okavango delta and may therefore substantially alter landscape connectivity in
this area. Besides a better understanding of the conservation needs for the
African wild dog, our study also presents a first step towards incorporating
environmental changes due to seasonality or climate change in dispersal and
connectivity analyses. Finally, our analysis demonstrates the usefulness of
individual-based dispersal simulations as a pertinent conservation tool to study
impacts of environmental change while accounting for dispersal movements.
